%-------------------------
% Resume in Latex
% Author : Abdullah Ozer
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{bold-extra}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\footskip}{4.5pt}
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Abdullah Ozer} \\ \vspace{5pt}
    {\LARGE \scshape Test Automation Engineer} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:33769929851}{+337 69 92 98 51}
    $|$
    \faAt \hspace{.5pt} \href{
      mailto:abdullahozer11@hotmail.com
    }{abdullahozer11@hotmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{
      https://www.linkedin.com/in/abdullah-ozer-a23733107/?locale=en_US
    }{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/abdullahozer11}{GitHub}
    $|$
    \faMapMarker \hspace{.5pt} \href{
      https://www.google.com/maps/place/Paris/@48.8588255,2.2646353,12z/data=!3m1!4b1!4m6!3m5!1s0x47e66e1f06e2b70f:0x40b82c3688c9460!8m2!3d48.856614!4d2.3522219!16zL20vMDVxdGo?entry=ttu
    }{Paris, France}
\end{center}



%----------- PROJECTS -----------

\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {6WIND}{Paris, France}
      {Test Automation Engineer (3 years)}
      {Aug 2021 \textbf{--} Ongoing, Full-time}
        \resumeItemListStart
            \resumeItem{
              Designed and implemented Python-based test automation framework for network software validation, significantly improving test coverage and reliability.
            }
            \resumeItem{
              Developed complex test scenarios simulating client infrastructures involving advanced networking protocols including IPSec, MPLS, BGP, VLAN, VXLAN, and GRE.
            }
            \resumeItem{
              Created and maintained automated performance testing suites to validate network KPIs including throughput, latency, and packet processing capabilities.
            }
            \resumeItem{
              Implemented CI/CD pipelines and developed custom testing tools using Python to streamline the testing process.
            }
        \resumeItemListEnd

    \resumeSubheading
      {STMicroelectronics}{Grenoble, France}
      {Test Development Engineer (2 years)}
      {Aug 2019 \textbf{--} Aug 2021, Full-time}
        \resumeItemListStart
            \resumeItem{
              Developed Python-based test automation tools for RF component validation, integrating with various signal measurement equipment.
            }
            \resumeItem{
              Created automated test scripts for hardware validation and performance testing.
            }
            \resumeItem{
              Implemented custom Python libraries for test equipment control and data analysis.
            }
        \resumeItemListEnd

    \resumeSubheading
      {Airties Wireless Networks}{Istanbul, Türkiye}
      {Test Engineer (2 years)}
      {Feb 2016 \textbf{--} Feb 2018, Full-time}
        \resumeItemListStart
            \resumeItem{
              Engineered automated testing solutions using Python for network device testing.
            }
            \resumeItem{
              Developed automation tools for hardware control including automated charging stations and smart testing platforms.
            }
            \resumeItem{
              Created Python scripts for automated regression testing and performance validation.
            }
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Programming Languages:}{
          Python 3.6+, JavaScript (ES6), TypeScript, Bash, HTML 5, CSS 3, PostgreSQL
        } \\ \vspace{3pt}
        \textbf{Python Development:}{
          Django, Django REST Framework, Unittest
        } \\ \vspace{3pt}
        \textbf{Networking Protocols:}{
          IPSec, MPLS, BGP, VLAN, VXLAN, GRE, TCP/IP
        } \\ \vspace{3pt}
        \textbf{Testing Tools:}{
          Python Test Frameworks, Network Analyzers, CI/CD Tools
        } \\ \vspace{3pt}
        \textbf{Languages:}{
          English (full proficiency), French (full proficiency), Turkish (native)
        } \\ \vspace{3pt}
    }}
  \resumeSubHeadingListEnd

%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeEducationHeading
      {ESIGELEC}
      {Rouen, France}
      {Master of Science \textbf{--} Major: Embedding Electronic Systems}
      {Feb 2018 \textbf{--} Aug 2019}

    \resumeEducationHeading
      {Bogazici University}
      {Istanbul, Türkiye}
      {Bachelors \textbf{--} Major: Electric and Electronics Engineering}
      {Feb 2011 \textbf{--} Aug 2016}

  \resumeSubHeadingListEnd

%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
        {\textbf{Network Protocol Testing Framework} $|$ \emph{Python, PostgreSQL}}{}
          \resumeItemListStart
            \resumeItem{
              Developed a comprehensive Python-based framework for testing complex networking protocols and scenarios.
            }
            \resumeItem{
              Implemented automated test suites for validating IPSec tunnels, MPLS paths, and BGP routing configurations.
            }
            \resumeItem{
              Created custom reporting and analysis tools using PostgreSQL for test results management.
            }
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Automated Test Infrastructure} $|$ \emph{Python, Bash}}{}
          \resumeItemListStart
            \resumeItem{
              Built automated testing infrastructure for network performance validation.
            }
            \resumeItem{
              Developed Python scripts for test environment setup and tear-down automation.
            }
            \resumeItem{
              Created monitoring and logging systems for long-running test suites.
            }
          \resumeItemListEnd

    \resumeSubHeadingListEnd


\end{document}
